On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-02 main.tex
Updated Section 6
Abstract references

  Algorithms for deciding connectivity queries in real algebraic
  geometry have been developed in a series of papers
  \cite{a,b,c,d}. However, these algorithms are based in the
  arithmetic complexity model, and analyses of the bit complexity
  questions were left for future work.  Our results are an important
  first step in this analysis.

@@

Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{a,b,c,d}. However, these algorithms are based in the arithmetic complexity model, and bit complexity questions have been left for future work. As bit complexity provides a far more realistic model of computation compared to arithmetic complexity,  which only counts each operation at unit cost, our results therefore begin to fill an important missing gap in the research. 

>>>>

  Algorithms for deciding connectivity queries in real algebraic
  geometry have been developed in a series of papers
  \cite{EMP,SchostMohabBabySteps2011,SchostMohabBabySteps2014,TWT}. However, these algorithms are based in the
  arithmetic complexity model, and analyses of the bit complexity
  questions were left for future work.  Our results are an important
  first step in this analysis.

@@

Algorithms for deciding connectivity queries in real algebraic geometry have been developed in a series of papers \cite{EMP,SchostMohabBabySteps2011,SchostMohabBabySteps2014,TWT}. However, these algorithms are based in the arithmetic complexity model, and bit complexity questions have been left for future work. As bit complexity provides a far more realistic model of computation compared to arithmetic complexity,  which only counts each operation at unit cost, our results therefore begin to fill an important missing gap in the research. 
